%!TEX encoding = UTF8
%!TEX root =cv-llt.tex
\prefix{}
\begin{rubric}{Skills}

\noentry{2014 -- 2015}

\entry*[Languages]
	English, French, Italian and Spanish (mother tongue).
\entry*[Experimental techniques\hfill]
	 Mid-and Near-infrared, RAMAN, NMR, PIXE, Electron microscopy, X-ray diffraction, X-ray absorption, X-ray powder diffraction.
% \entry*[Coding\hfill]
% 	Python, Fortran, C, C++, IDL, \LaTeX, \ldots
% \entry*[Operating Systems]
% 	Unix, MacOS, Windows.
\entry*[Computer (experience)]
Computer software systems implementation; Software selection; Development of tutorial programs and educational material; Maintenance and distribution of packages; Interaction with users, troubleshooting; Artificial intelligence (evolutionary computing); Internet technology (website design and management); (Co)author of packages: OASYS, XOP, SHADOW, XRAYLIB.

\entry*[Computer (Software)]
\begin{itemize}
\item Operating Systems: Linux, MacOS, and Windows.
\item Office: Microsoft Office (Word, Excel, Powerpoint), OpenOffice, Latex, HTML.  
\item Programming Languages: FORTRAN77, Fortran95, C, C++.
\item Application languages: python , IDL.
\item Parallel programming: MPI.
\item Programming Graphical User Interfaces: PyQt, IDL, python.
\item Generic Applications: Mathematica, Statistica.
\item Specific Scientific Applications: Monte Carlo particle transport (EGS4, PENELOPE), Ab-initio simulations (MSXAN, CONTINUUM, Gaussian03)
\end{itemize}
\entry*[Misc.]
	Academic research, teaching, training, consultation, \LaTeX\ typesetting and publishing.
\end{rubric}
